Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2022-02-25 unimodular-covers.tex
Add files via upload

\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage{tkz-euclide}
\usetikzlibrary{intersections}
\usetkzobj{all}

@@

These results leave open the following important questions:

@@

\paco{added ref to Gubeladze}
Let us also mention the following recent results of Gubeladze~\cite{Gubeladze}.
In part (2), a polytope $P$ is called \emph{very ample} if the vertex cone $\cone(P-v)$ is contained in the translation $P-v$, for every vertex $v$ of $P$.

\begin{theorem}[Gubeladze~\cite{Gubeladze}]
Let $P$ be a lattice $3$-polytope. 
\begin{enumerate}
\item If $P=E\cap \Z^3$ for some (solid) ellipsoid $E$, then $P$ has a unimodular cover.
\item If $P$ is \emph{very ample} then the boundary of $P$ has a unimodular cover. That is, there are unimodular simplices contained in $P$ whose union contains $\partial P$.
\end{enumerate}
\end{theorem}

>>>>

\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage{tkz-euclide}
\usetikzlibrary{intersections}
%\usetkzobj{all}

@@

These results leave open the following important questions regarding parallelotopes:

@@

\paco{added ref to Gubeladze}
\giulia{changed it}

To date there are no known example of IDP $3$-polytopes without a unimodular cover. Recent work of Gubeladze~\cite{Gubeladze} shows that another class of IDP 3-polytopes has unimodular covers, lattice polytopes which are convex hulls of all lattice points inside an ellipsoid. It remains open in general whether the classes are distinct in dimension $3$. 
%Let us also mention the following recent results of Gubeladze~\cite{Gubeladze}.
%In part (2), a polytope $P$ is called \emph{very ample} if the vertex cone $\cone(P-v)$ is contained in the translation $P-v$, for every vertex $v$ of $P$.

%\begin{theorem}[Gubeladze~\cite{Gubeladze}]
%Let $P$ be a lattice $3$-polytope. 
%\begin{enumerate}
%\item If $P=E\cap \Z^3$ for some (solid) ellipsoid $E$, then $P$ has a unimodular cover.
%\item If $P$ is \emph{very ample} then the boundary of $P$ has a unimodular cover. That is, there are unimodular simplices contained in $P$ whose union contains $\partial P$.
%\end{enumerate}
%\end{theorem}
